---
title:   "CO2 - Clean Data"
authors: "Natalia D'Agosti & Facundo Danza" 
---

# Load the packages

First, we load the necessary pacakges:
```{r}
rm(list=ls())
gc()
```

Second, we load the packages
```{r}
# install.packages("pacman")
pacman::p_load(tidyverse, readODS, readxl)
#library(margins)
```

Third, we set the plotting theme:
```{r}
theme_set(theme_bw())
```

Then, we load the directories:
```{r}
dir        <- list()
dir$root   <- dirname(getwd())
dir$data   <- paste0(dirname(getwd()), "/Data/")
dir$fig    <- paste0(dirname(getwd()), "/figures/")
dir$tab    <- paste0(dirname(getwd()), "/Tables/")
dir$adme   <- paste0(dir$data,"ADME_electricity_production/")
```

Arrange the data of hydro, thermal, wind, solar, biomass, demand, exports and imports.
Append this data with the main one.

upload the databases:

#2021#
January
```{r}
January_2021 <- 
  read_ods(paste0(dir$adme, "2021_January.ods"), 
                  sheet=1 ,range="A3:M747") #upload the database

January_2021 <- January_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) #separate the data variable into year, month, day, and hour
January_2021 <- January_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
January_2021 <- January_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
January_2021 <- 
  January_2021 %>% dplyr::select(-c(6,7)) # eliminate the min and sec columns empty

#Do the same with the exports
January_2021_X <- read_ods(paste0(dir$adme, "2021_January.ods"), 
                                  sheet=6 ,range="A3:D747") 

January_2021_X <- January_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
January_2021_X <- January_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
January_2021_X <- January_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
January_2021_X <- January_2021_X %>% 
  dplyr::select(-c(1,6,7)) # eliminate the min and sec columns empty

#merge both datasbes
January_2021 <-  merge(January_2021, January_2021_X, 
                       by=c("year", "month", "day", "hour"))
```

February
```{r}
Feb_2021 <- read_ods(paste0(dir$adme,"2021_Feb.ods"), 
                     sheet=1 ,range="A3:M675") #upload the database

Feb_2021 <- Feb_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Feb_2021 <- Feb_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Feb_2021 <- Feb_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Feb_2021 <- Feb_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
Feb_2021_X <- read_ods(paste0(dir$adme,"2021_Feb.ods"), 
                       sheet=6 ,range="A3:D675") 

Feb_2021_X <- Feb_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Feb_2021_X <- Feb_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Feb_2021_X <- Feb_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Feb_2021_X <- Feb_2021_X %>% 
  dplyr::select(-c(1,6,7))
#merge both datasbes
Feb_2021 <-  merge(Feb_2021, Feb_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

March
```{r}
March_2021 <- read_ods(paste0(dir$adme,"2021_March.ods"), 
                       sheet=1 ,range="A3:M747") #upload the database

March_2021 <- March_2021 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
March_2021 <- March_2021 %>%  separate(day, c("day", "hour"), sep=" ")
March_2021 <- March_2021 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
March_2021 <- March_2021 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
March_2021_X <- read_ods(paste0(dir$adme,"2021_March.ods"),
                         sheet=6 ,range="A3:D747") 

March_2021_X <- March_2021_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
March_2021_X <- March_2021_X %>%  separate(day, c("day", "hour"), sep=" ")
March_2021_X <- March_2021_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
March_2021_X <- March_2021_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
March_2021 <-  merge(March_2021, March_2021_X, 
                     by=c("year", "month", "day", "hour"))
```

April
```{r}
April_2021 <- read_ods(paste0(dir$adme,"2021_April.ods"), 
                       sheet=1 ,range="A3:M723") #upload the database

April_2021 <- April_2021 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
April_2021 <- April_2021 %>%  separate(day, c("day", "hour"), sep=" ")
April_2021 <- April_2021 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
April_2021 <- April_2021 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
April_2021_X <- read_ods(paste0(dir$adme,"2021_April.ods"), 
                         sheet=6 ,range="A3:D723") 

April_2021_X <- April_2021_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
April_2021_X <- April_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
April_2021_X <- April_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
April_2021_X <- April_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
April_2021 <-  merge(April_2021, April_2021_X, 
                     by=c("year", "month", "day", "hour"))
```

May
```{r}
May_2021 <- read_ods(paste0(dir$adme,"2021_May.ods"),
                     sheet=1 ,range="A3:M747") #upload the database

May_2021 <- May_2021 %>%  separate(Fecha, c("year", "month", "day"), 
                                   sep="-", remove=FALSE) 
May_2021 <- May_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
May_2021 <- May_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
May_2021 <- May_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
May_2021_X <- read_ods(paste0(dir$adme,"2021_May.ods"), 
                       sheet=6 ,range="A3:D747") 

May_2021_X <- May_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
May_2021_X <- May_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
May_2021_X <- May_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
May_2021_X <- May_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
May_2021 <-  merge(May_2021, May_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

June
```{r}
June_2021 <- read_ods(paste0(dir$adme,"2021_June.ods"), 
                      sheet=1 ,range="A3:M723") #upload the database

June_2021 <- June_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
June_2021 <- June_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
June_2021 <- June_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
June_2021 <- June_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
June_2021_X <- read_ods(paste0(dir$adme,"2021_June.ods"), 
                        sheet=6 ,range="A3:D723") 

June_2021_X <- June_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
June_2021_X <- June_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
June_2021_X <- June_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
June_2021_X <- June_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
June_2021 <-  merge(June_2021, June_2021_X, 
                    by=c("year", "month", "day", "hour"))
```

July
```{r}
July_2021 <- read_ods(paste0(dir$adme,"2021_July.ods"), 
                      sheet=1 ,range="A3:M747") #upload the database

July_2021 <- July_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
July_2021 <- July_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
July_2021 <- July_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
July_2021 <- July_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
July_2021_X <- read_ods(paste0(dir$adme,"2021_July.ods"), 
                        sheet=6 ,range="A3:D747") 

July_2021_X <- July_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
July_2021_X <- July_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
July_2021_X <- July_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
July_2021_X <- July_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
July_2021 <-  merge(July_2021, July_2021_X, 
                    by=c("year", "month", "day", "hour"))
```

August
```{r}
Aug_2021 <- read_ods(paste0(dir$adme,"2021_August.ods"), 
                     sheet=1 ,range="A3:M747") #upload the database

Aug_2021 <- Aug_2021 %>%  separate(Fecha, c("year", "month", "day"), 
                                   sep="-", remove=FALSE) 
Aug_2021 <- Aug_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Aug_2021 <- Aug_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Aug_2021 <- Aug_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
Aug_2021_X <- read_ods(paste0(dir$adme,"2021_August.ods"), 
                       sheet=6 ,range="A3:D747") 

Aug_2021_X <- Aug_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Aug_2021_X <- Aug_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Aug_2021_X <- Aug_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Aug_2021_X <- Aug_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
Aug_2021 <-  merge(Aug_2021, Aug_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

September
```{r}
Sep_2021 <- read_ods(paste0(dir$adme,"2021_Sept.ods"), 
                     sheet=1 ,range="A3:M723") #upload the database

Sep_2021 <- Sep_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Sep_2021 <- Sep_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Sep_2021 <- Sep_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Sep_2021 <- Sep_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
Sep_2021_X <- read_ods(paste0(dir$adme,"2021_Sept.ods"), 
                       sheet=6 ,range="A3:D723") 

Sep_2021_X <- Sep_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Sep_2021_X <- Sep_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Sep_2021_X <- Sep_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Sep_2021_X <- Sep_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
Sep_2021 <-  merge(Sep_2021, Sep_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

October
```{r}
Oct_2021 <- read_ods(paste0(dir$adme,"2021_Oct.ods"), 
                     sheet=1 ,range="A3:M747") #upload the database

Oct_2021 <- Oct_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Oct_2021 <- Oct_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Oct_2021 <- Oct_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Oct_2021 <- Oct_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
Oct_2021_X <- read_ods(paste0(dir$adme,"2021_Oct.ods"), 
                       sheet=6 ,range="A3:D747") 

Oct_2021_X <- Oct_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Oct_2021_X <- Oct_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Oct_2021_X <- Oct_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Oct_2021_X <- Oct_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
Oct_2021 <-  merge(Oct_2021, Oct_2021_X, by=c("year", "month", "day", "hour"))
```

November
```{r}
Nov_2021 <- read_ods(paste0(dir$adme,"2021_Nov.ods"), 
                     sheet=1 ,range="A3:M723") #upload the database

Nov_2021 <- Nov_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Nov_2021 <- Nov_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Nov_2021 <- Nov_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Nov_2021 <- Nov_2021 %>% 
  dplyr::select(-c(6,7)) 

#Do the same with the exports
Nov_2021_X <- read_ods(paste0(dir$adme,"2021_Nov.ods"), 
                       sheet=6 ,range="A3:D723") 

Nov_2021_X <- Nov_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Nov_2021_X <- Nov_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Nov_2021_X <- Nov_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Nov_2021_X <- Nov_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
Nov_2021 <-  merge(Nov_2021, Nov_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

December
```{r}
Dec_2021 <- read_ods(paste0(dir$adme,"2021_Dec.ods"), 
                     sheet=1 ,range="A3:M747") #upload the database

Dec_2021 <- Dec_2021 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Dec_2021 <- Dec_2021 %>%  
  separate(day, c("day", "hour"), sep=" ")
Dec_2021 <- Dec_2021 %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Dec_2021 <- Dec_2021 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
Dec_2021_X <- read_ods(paste0(dir$adme,"2021_Dec.ods"), 
                       sheet=6 ,range="A3:D747") 

Dec_2021_X <- Dec_2021_X %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Dec_2021_X <- Dec_2021_X %>%  
  separate(day, c("day", "hour"), sep=" ")
Dec_2021_X <- Dec_2021_X %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
Dec_2021_X <- Dec_2021_X %>% 
  dplyr::select(-c(1,6,7)) 

#merge both datasbes
Dec_2021 <-  merge(Dec_2021, Dec_2021_X, 
                   by=c("year", "month", "day", "hour"))
```

#2022#

January
```{r}
January_2022 <- read_ods(paste0(dir$adme, "2022_January.ods"), 
                         sheet=1 ,range="A3:M747") #upload the database

January_2022 <- January_2022 %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) #separate the data variable into year, month, day, and hour
January_2022 <- January_2022 %>%  
  separate(day, c("day", "hour"), sep=" ")
January_2022 <- January_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
January_2022 <- January_2022 %>% dplyr::select(-c(6,7)) # eliminate the min and sec columns empty

#Do the same with the exports
January_2022_X <- read_ods(paste0(dir$adme,"2022_January.ods"),
                           sheet=6 ,range="A3:D747") 

January_2022_X <- January_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
January_2022_X <- January_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
January_2022_X <- January_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
January_2022_X <- January_2022_X %>% dplyr::select(-c(1,6,7)) # eliminate the min and sec columns empty

#merge both datasbes
January_2022 <-  merge(January_2022, January_2022_X, by=c("year", "month", "day", "hour"))
```

February
```{r}
Feb_2022 <- read_ods(paste0(dir$adme,"2022_Feb.ods"),
                     sheet=1 ,range="A3:M675") #upload the database

Feb_2022 <- Feb_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Feb_2022 <- Feb_2022 %>%  separate(day, c("day", "hour"), sep=" ")
Feb_2022 <- Feb_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
Feb_2022 <- Feb_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
Feb_2022_X <- read_ods(paste0(dir$adme, "2022_Feb.ods"),
                       sheet=6 ,range="A3:D675") 

Feb_2022_X <- Feb_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Feb_2022_X <- Feb_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
Feb_2022_X <- Feb_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
Feb_2022_X <- Feb_2022_X %>% dplyr::select(-c(1,6,7))
#merge both datasbes
Feb_2022 <-  merge(Feb_2022, Feb_2022_X, by=c("year", "month", "day", "hour"))
```

March
```{r}
March_2022 <- read_ods(paste0(dir$adme,"2022_March.ods"),
                       sheet=1 ,range="A3:M747") #upload the database

March_2022 <- March_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
March_2022 <- March_2022 %>%  separate(day, c("day", "hour"), sep=" ")
March_2022 <- March_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
March_2022 <- March_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
March_2022_X <- read_ods(paste0(dir$adme,"2022_March.ods"),
                         sheet=6 ,range="A3:D747") 

March_2022_X <- March_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
March_2022_X <- March_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
March_2022_X <- March_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
March_2022_X <- March_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
March_2022 <-  merge(March_2022, March_2022_X, by=c("year", "month", "day", "hour"))
```

April
```{r}
April_2022 <- read_ods(paste0(dir$adme,"2022_April.ods")
                       , sheet=1 ,range="A3:M723") #upload the database

April_2022 <- April_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
April_2022 <- April_2022 %>%  separate(day, c("day", "hour"), sep=" ")
April_2022 <- April_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
April_2022 <- April_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
April_2022_X <- read_ods(paste0(dir$adme,"2022_April.ods"),
                         sheet=6 ,range="A3:D723") 

April_2022_X <- April_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
April_2022_X <- April_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
April_2022_X <- April_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
April_2022_X <- April_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
April_2022 <-  merge(April_2022, April_2022_X, by=c("year", "month", "day", "hour"))
```

May
```{r}
May_2022 <- read_ods(paste0(dir$adme, "2022_May.ods"),
                     sheet=1 ,range="A3:M747") #upload the database

May_2022 <- May_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
May_2022 <- May_2022 %>%  separate(day, c("day", "hour"), sep=" ")
May_2022 <- May_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
May_2022 <- May_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
May_2022_X <- read_ods(paste0(dir$adme,"2022_May.ods"),
                       sheet=6 ,range="A3:D747") 

May_2022_X <- May_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
May_2022_X <- May_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
May_2022_X <- May_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
May_2022_X <- May_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
May_2022 <-  merge(May_2022, May_2022_X, by=c("year", "month", "day", "hour"))
```

June
```{r}
June_2022 <- read_ods(paste0(dir$adme,"2022_June.ods"),
                      sheet=1 ,range="A3:M723") #upload the database

June_2022 <- June_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
June_2022 <- June_2022 %>%  separate(day, c("day", "hour"), sep=" ")
June_2022 <- June_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
June_2022 <- June_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
June_2022_X <- read_ods(paste0(dir$adme,"2022_June.ods"), 
                        sheet=6 ,range="A3:D723") 

June_2022_X <- June_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
June_2022_X <- June_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
June_2022_X <- June_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
June_2022_X <- June_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
June_2022 <-  merge(June_2022, June_2022_X, by=c("year", "month", "day", "hour"))
```

July
```{r}
July_2022 <- read_ods(paste0(dir$adme,"2022_July.ods"),
                      sheet=1 ,range="A3:M747") #upload the database

July_2022 <- July_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
July_2022 <- July_2022 %>%  separate(day, c("day", "hour"), sep=" ")
July_2022 <- July_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
July_2022 <- July_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
July_2022_X <- read_ods(paste0(dir$adme,"2022_July.ods"), 
                        sheet=6 ,range="A3:D747") 

July_2022_X <- July_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
July_2022_X <- July_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
July_2022_X <- July_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
July_2022_X <- July_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
July_2022 <-  merge(July_2022, July_2022_X, by=c("year", "month", "day", "hour"))
```

August
```{r}
Aug_2022 <- read_ods(paste0(dir$adme,"2022_August.ods"),
                     sheet=1 ,range="A3:M747") #upload the database

Aug_2022 <- Aug_2022 %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Aug_2022 <- Aug_2022 %>%  separate(day, c("day", "hour"), sep=" ")
Aug_2022 <- Aug_2022 %>%  separate(hour, c("hour", "min", "sec"), sep=":")
Aug_2022 <- Aug_2022 %>% dplyr::select(-c(6,7)) 

#Do the same with the exports
Aug_2022_X <- read_ods(paste0(dir$adme,"2022_August.ods"), sheet=6 ,range="A3:D747") 

Aug_2022_X <- Aug_2022_X %>%  separate(Fecha, c("year", "month", "day"), sep="-", remove=FALSE) 
Aug_2022_X <- Aug_2022_X %>%  separate(day, c("day", "hour"), sep=" ")
Aug_2022_X <- Aug_2022_X %>%  separate(hour, c("hour", "min", "sec"), sep=":")
Aug_2022_X <- Aug_2022_X %>% dplyr::select(-c(1,6,7)) 

#merge both datasbes
Aug_2022 <-  merge(Aug_2022, Aug_2022_X, by=c("year", "month", "day", "hour"))
```


Append all 2021
```{r}
final_2021 <- rbind(January_2021, Feb_2021, March_2021, April_2021, May_2021, June_2021, July_2021, Aug_2021, Sep_2021, Oct_2021, Nov_2021, Dec_2021)
```

Append all 2022
```{r}
final_2022 <- rbind(January_2022, Feb_2022, March_2022, April_2022, May_2022, June_2022, July_2022, Aug_2022)
```


Eliminate the extra DF
```{r}
rm(January_2021_X, Feb_2021_X, March_2021_X, April_2021_X, May_2021_X, June_2021_X, July_2021_X, Aug_2021_X, Sep_2021_X, Oct_2021_X, Nov_2021_X, Dec_2021_X, January_2022_X, Feb_2022_X, March_2022_X, April_2022_X, May_2022_X, June_2022_X, July_2022_X, Aug_2022_X, January_2021, Feb_2021, March_2021, April_2021, May_2021, June_2021, July_2021, Aug_2021, Sep_2021, Oct_2021, Nov_2021, Dec_2021, January_2022, Feb_2022, March_2022, April_2022, May_2022, June_2022, July_2022, Aug_2022)
```

Generate total imports, exports and hydro
```{r}
final_2021 <- final_2021 %>% rename("sg" = "Salto Grande")
final_2021 <- final_2021 %>% mutate(hydro = sg + Palmar + Bonete + Baygorria)
final_2021 <- final_2021 %>% mutate(total_imports = Imp.Arg + Imp.Br.Riv + Imp.Br.Mel)
final_2021 <- final_2021 %>% mutate(total_exports = Exp_Intercon_BR_MELO + Exp_Intercon_BR_RIVERA + Exp_Intercon_ARG)

final_2022 <- final_2022 %>% rename("sg" = "Salto Grande")
final_2022 <- final_2022 %>% mutate(hydro = sg + Palmar + Bonete + Baygorria)
final_2022 <- final_2022 %>% mutate(total_imports = Imp.Arg + Imp.Br.Riv + Imp.Br.Mel)
final_2022 <- final_2022 %>% mutate(total_exports = Exp_Intercon_BR_MELO + Exp_Intercon_BR_RIVERA + Exp_Intercon_ARG)

```


change the names:
```{r}
final_2021 <- final_2021 %>% 
  rename("wind"="Eólica", "solar"="Solar", "thermal"="Térmica", "biomass"="Biomasa", "demand"="Demanda")

final_2022 <- final_2022 %>% 
  rename("wind"="Eólica", "solar"="Solar", "thermal"="Térmica", "biomass"="Biomasa", "demand"="Demanda")
```

Select only those variables that I need and convert all the year, month, day, hour in numbers
```{r}
final_2021 <- final_2021 %>% dplyr::select(-c(5, 6, 7, 8, 9, 14, 15, 16, 18, 19, 20))
final_2022 <- final_2022 %>% dplyr::select(-c(5, 6, 7, 8, 9, 14, 15, 16, 18, 19, 20))

final_2021$year <- as.numeric(final_2021$year)
final_2021$month <- as.numeric(final_2021$month)
final_2021$day <- as.numeric(final_2021$day)
final_2021$hour <- as.numeric(final_2021$hour)

final_2022$year <- as.numeric(final_2022$year)
final_2022$month <- as.numeric(final_2022$month)
final_2022$day <- as.numeric(final_2022$day)
final_2022$hour <- as.numeric(final_2022$hour)

```

Save the databases:
```{r}
save(final_2021, file=paste0(dir$adme,"final_2021.RData"))
save(final_2022, file=paste0(dir$adme,"final_2022.RData"))
```


# Arrange the Demand

Problem: CTM - Salto Grande, if it is negative, then it goes to exports, so it is computed double - in hydro production and in exports.
Thus, I need to sum it positive twice (once from the hydro production, and once from the exports)
(T + H + B + W + S + IM + Microgenerators = D + EX)
So I will get the year, month, day, hour, and Negative CTM


year 2018:
```{r}
UY_2018 <- 
  read_excel(paste0(dir$data,"Renewable-Energy-UY-main/gpf 2018.xlsx"), 
             sheet=1 ,range="A4:N8764")
UY_2019 <- 
  read_excel(paste0(dir$data,"Renewable-Energy-UY-main/gpf 2019.xlsx"), 
             sheet=1 ,range="A4:N8764")
UY_2020 <- 
  read_excel(paste0(dir$data,"Renewable-Energy-UY-main/gpf 2020.xlsx"),
             sheet=1 ,range="A4:N8788")
UY_2021 <- 
  read_excel(paste0(dir$data,"Renewable-Energy-UY-main/gpf 2021 01_06.xlsx"), 
             sheet=1 ,range="A4:N3652")
```


Append the data:
```{r}
final_data_CTM <- 
  rbind(UY_2019, UY_2020, UY_2021, UY_2018)
final_data_CTM <- 
  final_data_CTM %>% dplyr::select("Fecha", "CTM-UR")
final_data_CTM <- 
  final_data_CTM %>% rename("CTM"="CTM-UR")
final_data_CTM <- 
  final_data_CTM %>% filter(CTM<0)
```

```{r}
final_data_CTM <- final_data_CTM %>%  
  separate(Fecha, c("year", "month", "day"), sep="-", remove=TRUE)
final_data_CTM <- final_data_CTM %>%  
  separate(day, c("day", "hour"), sep=" ")
final_data_CTM <- final_data_CTM %>%  
  separate(hour, c("hour", "min", "sec"), sep=":")
final_data_CTM <- final_data_CTM %>% 
  dplyr::select(-c(5,6)) # eliminate the min and sec columns empty

final_data_CTM$hour <- 
  as.numeric(final_data_CTM$hour)
final_data_CTM$day <- 
  as.numeric(final_data_CTM$day)
final_data_CTM$month <- as.numeric(final_data_CTM$month)
final_data_CTM$year <- as.numeric(final_data_CTM$year)
```

```{r}
save(final_data_CTM, 
     file=paste0(dir$data,"Gurobi/CTM_Gurobi.RData"))
```

