---
title: "Clean Data - CO2"
authors: "Natalia D'Agosti & Facundo Danza" 
---

# Load the packages

First, we load the necessary pacakges:
```{r}
rm(list=ls())
gc()
```

Second, we load the packages
```{r}
# install.packages("pacman")
pacman::p_load(tidyverse, lubridate, readxl, 
               sandwich, arm, fixest, gapminder, car)
#library(margins)
```

Third, we set the plotting theme:
```{r}
theme_set(theme_bw())
```

Then, we load the directories:
```{r}
dir        <- list()
dir$root   <- dirname(getwd())
dir$data   <- paste0(dirname(getwd()), "/Data/")
dir$fig    <- paste0(dirname(getwd()), "/figures/")
dir$tab    <- paste0(dirname(getwd()), "/Tables/")
```


# First Analysis 

Arrange the injection data to use it in the Gurobi optimization problem.

The data is of electricity injected into the grid is at household level at monthly level
First, I add all the microgenerators - thus, I know the total of electricity inyected in a certain month

Now I have to transform this data from monthly to hourly.

Use the injection data of electricity into the grid:

```{r}
load(paste0(dir$data,
            "Gurobi/inyection_data.RData"))
```

Eliminate some variables:
```{r}
#which days are the electricity injected to the grid bigger than zero: From November 2018 to August 2022
final_inyection <- 
  iny_res %>% 
  filter(ener_iny > 0) %>%
  group_by(year, month, day) %>%  
  summarize(ener_iny=sum(ener_iny, 
                         na.rm=TRUE))  %>% 
  ungroup()
# sum all the microgenerators that are injecting in a specific month

#convert the data to numeric
final_inyection <- 
  final_inyection %>%
  mutate(across(c('year', 'month', 'day'), 
                as.numeric))
```

 

Do the same bur instead of assuming a uniformly distribution, assume a normal one:

Arrange the injection data to use it in the Gurobi optimization problem.
The data is of electricity injected into the grid is at household level at monthly level
First, I add all the microgenerators - thus, I know the total of electricity inyected in a certain month

Keep the first row: add it more days and hours

## 2018
1) First row is November - 2018 
```{r}
nov_2018 <- final_inyection[1,]

nov_2018 <- nov_2018 %>% mutate(day=1, hour=0) #create the variable day
nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 30), ] #multiplies each row 30 times
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 24), ] #For each day, add 24 hours
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

#If, the energy inyected is positive, then between 18 pm until 7 am is equal zero, and between 8 am to 17 pm is the electricity inyected/300. 
#Why 23. The first 23, is to find the electricity inyected by day (eliminating those days which the thermal is equal zero)
nov_2018 <- nov_2018 %>% mutate(elec_inyected =  ener_iny/(30-7))

nov_2018 <- nov_2018 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

2) December - 2018
```{r}
dec_2018 <- final_inyection[2,]

dec_2018 <- dec_2018 %>% mutate(day=1, hour=0) #create the variable day
dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 31), ] #multiplies each row 30 times
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 24), ] #For each day, add 24 hours
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2018 <- dec_2018 %>% mutate(elec_inyected =  ener_iny/(31-5))

dec_2018 <- dec_2018 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


```{r}
elec_inyection_2018 <- rbind(nov_2018, dec_2018)
rm(nov_2018, dec_2018)
```


## 2019

3) January - 2019
```{r}
jan_2019 <- final_inyection[3,]

jan_2019 <- jan_2019 %>% mutate(day=1, hour=0) #create the variable day
jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 31), ] #multiplies each row 30 times
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 24), ] #For each day, add 24 hours
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2019 <- jan_2019 %>% mutate(elec_inyected = ener_iny/(31-2))

jan_2019 <- jan_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

4) February - 2019
```{r}
feb_2019 <- final_inyection[4,]

feb_2019 <- feb_2019 %>% mutate(day=1, hour=0) #create the variable day
feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 28), ] #multiplies each row 30 times
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 24), ] #For each day, add 24 hours
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2019 <- feb_2019 %>% mutate(elec_inyected =  ener_iny/(28-2))

feb_2019 <- feb_2019 %>% mutate(elec_inyected= elec_inyected/1000) # change from the electricity inyected from KWh to MWh
```

5) March - 2019
```{r}
mar_2019 <- final_inyection[5,]

mar_2019 <- mar_2019 %>% mutate(day=1, hour=0) #create the variable day
mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 31), ] #multiplies each row 30 times
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 24), ] #For each day, add 24 hours
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2019 <- mar_2019 %>% mutate(elec_inyected = ener_iny/(31-10))

mar_2019 <- mar_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


6) April - 2019 
```{r}
apr_2019 <- final_inyection[6,]

apr_2019 <- apr_2019 %>% mutate(day=1, hour=0) #create the variable day
apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 30), ] #multiplies each row 30 times
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 24), ] #For each day, add 24 hours
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2019 <- apr_2019 %>% mutate(elec_inyected = ener_iny/(30-20))

apr_2019 <- apr_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

7) May - 2019
```{r}
may_2019 <- final_inyection[7,]

may_2019 <- may_2019 %>% mutate(day=1, hour=0) #create the variable day
may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 31), ] #multiplies each row 30 times
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 24), ] #For each day, add 24 hours
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2019 <- may_2019 %>% mutate(elec_inyected =  ener_iny/(31-19))

may_2019 <- may_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

8) June - 2019 
```{r}
june_2019 <- final_inyection[8,]

june_2019 <- june_2019 %>% mutate(day=1, hour=0) #create the variable day
june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 30), ] #multiplies each row 30 times
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 24), ] #For each day, add 24 hours
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2019 <- june_2019 %>% mutate(elec_inyected = ener_iny/(30-18))

june_2019 <- june_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

9) July - 2019
```{r}
july_2019 <- final_inyection[9,]

july_2019 <- july_2019 %>% mutate(day=1, hour=0) #create the variable day
july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 31), ] #multiplies each row 30 times
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 24), ] #For each day, add 24 hours
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2019 <- july_2019 %>% mutate(elec_inyected =  ener_iny/(31-15))

july_2019 <- july_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

10) August - 2019 
```{r}
aug_2019 <- final_inyection[10,]

aug_2019 <- aug_2019 %>% mutate(day=1, hour=0) #create the variable day
aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 31), ] #multiplies each row 30 times
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 24), ] #For each day, add 24 hours
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2019 <- aug_2019 %>% mutate(elec_inyected = ener_iny/(31-12))

aug_2019 <- aug_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

11) September - 2019 
```{r}
sep_2019 <- final_inyection[11,]

sep_2019 <- sep_2019 %>% mutate(day=1, hour=0) #create the variable day
sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 30), ] #multiplies each row 30 times
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 24), ] #For each day, add 24 hours
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2019 <- sep_2019 %>% mutate(elec_inyected =  ener_iny/(30-7))

sep_2019 <- sep_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

12) October - 2019 
```{r}
oct_2019 <- final_inyection[12,]

oct_2019 <- oct_2019 %>% mutate(day=1, hour=0) #create the variable day
oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 31), ] #multiplies each row 30 times
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 24), ] #For each day, add 24 hours
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2019 <- oct_2019 %>% mutate(elec_inyected = ener_iny/(31-12))

oct_2019 <- oct_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

13) November - 2019 
```{r}
nov_2019 <- final_inyection[13,]

nov_2019 <- nov_2019 %>% mutate(day=1, hour=0) #create the variable day
nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 30), ] #multiplies each row 30 times
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 24), ] #For each day, add 24 hours
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2019 <- nov_2019 %>% mutate(elec_inyected =  ener_iny/(30-20))

nov_2019 <- nov_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

14) December - 2019 
```{r}
dec_2019 <- final_inyection[14,]

dec_2019 <- dec_2019 %>% mutate(day=1, hour=0) #create the variable day
dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 31), ] #multiplies each row 30 times
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 24), ] #For each day, add 24 hours
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2019 <- dec_2019 %>% mutate(elec_inyected = ener_iny/(31-21))

dec_2019 <- dec_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


```{r}
elec_inyection_2019 <- rbind(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
rm(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
```

## 2020

15) January - 2020 
```{r}
jan_2020 <- final_inyection[15,]

jan_2020 <- jan_2020 %>% mutate(day=1, hour=0) #create the variable day
jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 31), ] #multiplies each row 30 times
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 24), ] #For each day, add 24 hours
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2020 <- jan_2020 %>% mutate(elec_inyected =  ener_iny/(31-15))

jan_2020 <- jan_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

16) February - 2020
```{r}
feb_2020 <- final_inyection[16,]

feb_2020 <- feb_2020 %>% mutate(day=1, hour=0) #create the variable day
feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 29), ] #multiplies each row 30 times
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(day=1:29) # add days from 1 to 30

feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 24), ] #For each day, add 24 hours
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2020 <- feb_2020 %>% mutate(elec_inyected = ener_iny/(29-9))

feb_2020 <- feb_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

17) March - 2020 
```{r}
mar_2020 <- final_inyection[17,]

mar_2020 <- mar_2020 %>% mutate(day=1, hour=0) #create the variable day
mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 31), ] #multiplies each row 30 times
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 24), ] #For each day, add 24 hours
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2020 <- mar_2020 %>% mutate(elec_inyected = ener_iny/(31-9))

mar_2020 <- mar_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

18) April 2020 
```{r}
apr_2020 <- final_inyection[18,]

apr_2020 <- apr_2020 %>% mutate(day=1, hour=0) #create the variable day
apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 30), ] #multiplies each row 30 times
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 24), ] #For each day, add 24 hours
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2020 <- apr_2020 %>% mutate(elec_inyected = ener_iny/(30-23))

apr_2020 <- apr_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

19) May - 2020 
```{r}
may_2020 <- final_inyection[19,]

may_2020 <- may_2020 %>% mutate(day=1, hour=0) #create the variable day
may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 31), ] #multiplies each row 30 times
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 24), ] #For each day, add 24 hours
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2020 <- may_2020 %>% mutate(elec_inyected = ener_iny/(31-25))

may_2020 <- may_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

20) June 2020 
```{r}
june_2020 <- final_inyection[20,]

june_2020 <- june_2020 %>% mutate(day=1, hour=0) #create the variable day
june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 30), ] #multiplies each row 30 times
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 24), ] #For each day, add 24 hours
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2020 <- june_2020 %>% mutate(elec_inyected = ener_iny/(30-17))

june_2020 <- june_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```


21) July - 2020 
```{r}
july_2020 <- final_inyection[21,]

july_2020 <- july_2020 %>% mutate(day=1, hour=0) #create the variable day
july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 31), ] #multiplies each row 30 times
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 24), ] #For each day, add 24 hours
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2020 <- july_2020 %>% mutate(elec_inyected = ener_iny/(31-14))

july_2020 <- july_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

22) August - 2020 
```{r}
aug_2020 <- final_inyection[22,]

aug_2020 <- aug_2020 %>% mutate(day=1, hour=0) #create the variable day
aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 31), ] #multiplies each row 30 times
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 24), ] #For each day, add 24 hours
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2020 <- aug_2020 %>% mutate(elec_inyected = ener_iny/(31-21))

aug_2020 <- aug_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

23) September 2020 
```{r}
sep_2020 <- final_inyection[23,]

sep_2020 <- sep_2020 %>% mutate(day=1, hour=0) #create the variable day
sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 30), ] #multiplies each row 30 times
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 24), ] #For each day, add 24 hours
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2020 <- sep_2020 %>% mutate(elec_inyected =  ener_iny/(30-24))

sep_2020 <- sep_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

24) October - 2020 
```{r}
oct_2020 <- final_inyection[24,]

oct_2020 <- oct_2020 %>% mutate(day=1, hour=0) #create the variable day
oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 31), ] #multiplies each row 30 times
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 24), ] #For each day, add 24 hours
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2020 <- oct_2020 %>% mutate(elec_inyected = ener_iny/(31-12))

oct_2020 <- oct_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

25) November 2020 
```{r}
nov_2020 <- final_inyection[25,]

nov_2020 <- nov_2020 %>% mutate(day=1, hour=0) #create the variable day
nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 30), ] #multiplies each row 30 times
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 24), ] #For each day, add 24 hours
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2020 <- nov_2020 %>% mutate(elec_inyected =  ener_iny/(30-3))

nov_2020 <- nov_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

26) December - 2020 
```{r}
dec_2020 <- final_inyection[26,]

dec_2020 <- dec_2020 %>% mutate(day=1, hour=0) #create the variable day
dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 31), ] #multiplies each row 30 times
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 24), ] #For each day, add 24 hours
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2020 <- dec_2020 %>% mutate(elec_inyected = ener_iny/(31-2))

dec_2020 <- dec_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2020 <- rbind(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
rm(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
```

## 2021
27) January - 2021 
```{r}
jan_2021 <- final_inyection[27,]

jan_2021 <- jan_2021 %>% mutate(day=1, hour=0) #create the variable day
jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 31), ] #multiplies each row 30 times
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 24), ] #For each day, add 24 hours
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2021 <- jan_2021 %>% mutate(elec_inyected =  ener_iny/(31-5))

jan_2021 <- jan_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

28) February - 2021
```{r}
feb_2021 <- final_inyection[28,]

feb_2021 <- feb_2021 %>% mutate(day=1, hour=0) #create the variable day
feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 28), ] #multiplies each row 30 times
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 24), ] #For each day, add 24 hours
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2021 <- feb_2021 %>% mutate(elec_inyected =  ener_iny/(28-9))

feb_2021 <- feb_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

29) March - 2021 
```{r}
mar_2021 <- final_inyection[29,]

mar_2021 <- mar_2021 %>% mutate(day=1, hour=0) #create the variable day
mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 31), ] #multiplies each row 30 times
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 24), ] #For each day, add 24 hours
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2021 <- mar_2021 %>% mutate(elec_inyected =  ener_iny/31)

mar_2021 <- mar_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

30) April 2021 
```{r}
apr_2021 <- final_inyection[30,]

apr_2021 <- apr_2021 %>% mutate(day=1, hour=0) #create the variable day
apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 30), ] #multiplies each row 30 times
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 24), ] #For each day, add 24 hours
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2021 <- apr_2021 %>% mutate(elec_inyected =  ener_iny/(30-7))

apr_2021 <- apr_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

31) May - 2021 
```{r}
may_2021 <- final_inyection[31,]

may_2021 <- may_2021 %>% mutate(day=1, hour=0) #create the variable day
may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 31), ] #multiplies each row 30 times
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 24), ] #For each day, add 24 hours
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2021 <- may_2021 %>% mutate(elec_inyected =  ener_iny/(31-4))

may_2021 <- may_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

32) June 2021 
```{r}
june_2021 <- final_inyection[32,]

june_2021 <- june_2021 %>% mutate(day=1, hour=0) #create the variable day
june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 30), ] #multiplies each row 30 times
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 24), ] #For each day, add 24 hours
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2021 <- june_2021 %>% mutate(elec_inyected =  ener_iny/(30-7))

june_2021 <- june_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


33) July - 2021 
```{r}
july_2021 <- final_inyection[33,]

july_2021 <- july_2021 %>% mutate(day=1, hour=0) #create the variable day
july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 31), ] #multiplies each row 30 times
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 24), ] #For each day, add 24 hours
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2021 <- july_2021 %>% mutate(elec_inyected =  ener_iny/(31-7))

july_2021 <- july_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

34) August - 2021 
```{r}
aug_2021 <- final_inyection[34,]

aug_2021 <- aug_2021 %>% mutate(day=1, hour=0) #create the variable day
aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 31), ] #multiplies each row 30 times
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 24), ] #For each day, add 24 hours
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2021 <- aug_2021 %>% mutate(elec_inyected = ener_iny/31)

aug_2021 <- aug_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

35) September 2021 
```{r}
sep_2021 <- final_inyection[35,]

sep_2021 <- sep_2021 %>% mutate(day=1, hour=0) #create the variable day
sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 30), ] #multiplies each row 30 times
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 24), ] #For each day, add 24 hours
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2021 <- sep_2021 %>% mutate(elec_inyected =  ener_iny/30)

sep_2021 <- sep_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

36) October - 2021 
```{r}
oct_2021 <- final_inyection[36,]

oct_2021 <- oct_2021 %>% mutate(day=1, hour=0) #create the variable day
oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 31), ] #multiplies each row 30 times
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 24), ] #For each day, add 24 hours
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2021 <- oct_2021 %>% mutate(elec_inyected =  ener_iny/31)

oct_2021 <- oct_2021 %>% mutate(elec_inyected= elec_inyected/1000) # changefrom the electricity inyected from KWh to MWh
```

37) November 2021 
```{r}
nov_2021 <- final_inyection[37,]

nov_2021 <- nov_2021 %>% mutate(day=1, hour=0) #create the variable day
nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 30), ] #multiplies each row 30 times
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 24), ] #For each day, add 24 hours
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2021 <- nov_2021 %>% mutate(elec_inyected =  ener_iny/30)

nov_2021 <- nov_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

38) December - 2021 
```{r}
dec_2021 <- final_inyection[38,]

dec_2021 <- dec_2021 %>% mutate(day=1, hour=0) #create the variable day
dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 31), ] #multiplies each row 30 times
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 24), ] #For each day, add 24 hours
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2021 <- dec_2021 %>% mutate(elec_inyected =  ener_iny/31)

dec_2021 <- dec_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2021 <- rbind(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
rm(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
```

## 2022
39) January - 2022
```{r}
jan_2022 <- final_inyection[39,]

jan_2022 <- jan_2022 %>% mutate(day=1, hour=0) #create the variable day
jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 31), ] #multiplies each row 30 times
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 24), ] #For each day, add 24 hours
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2022 <- jan_2022 %>% mutate(elec_inyected = ener_iny/31)

jan_2022 <- jan_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

40) February - 2022
```{r}
feb_2022 <- final_inyection[40,]

feb_2022 <- feb_2022 %>% mutate(day=1, hour=0) #create the variable day
feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 28), ] #multiplies each row 30 times
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 24), ] #For each day, add 24 hours
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2022 <- feb_2022 %>% mutate(elec_inyected =  ener_iny/28)

feb_2022 <- feb_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

41) March - 2022
```{r}
mar_2022 <- final_inyection[41,]

mar_2022 <- mar_2022 %>% mutate(day=1, hour=0) #create the variable day
mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 31), ] #multiplies each row 30 times
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 24), ] #For each day, add 24 hours
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2022 <- mar_2022 %>% mutate(elec_inyected =  ener_iny/(31-3))

mar_2022 <- mar_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

42) April 2022 
```{r}
apr_2022 <- final_inyection[42,]

apr_2022 <- apr_2022 %>% mutate(day=1, hour=0) #create the variable day
apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 30), ] #multiplies each row 30 times
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 24), ] #For each day, add 24 hours
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2022 <- apr_2022 %>% mutate(elec_inyected =  ener_iny/(30-17))

apr_2022 <- apr_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

43) May - 2022 
```{r}
may_2022 <- final_inyection[43,]

may_2022 <- may_2022 %>% mutate(day=1, hour=0) #create the variable day
may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 31), ] #multiplies each row 30 times
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 24), ] #For each day, add 24 hours
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2022 <- may_2022 %>% mutate(elec_inyected =  ener_iny/(31-11))

may_2022 <- may_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity injected from KWh to MWh
```

44) June 2022 
```{r}
june_2022 <- final_inyection[44,]

june_2022 <- june_2022 %>% mutate(day=1, hour=0) #create the variable day
june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 30), ] #multiplies each row 30 times
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 24), ] #For each day, add 24 hours
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2022 <- june_2022 %>% mutate(elec_inyected =  ener_iny/(30-5))

june_2022 <- june_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```


45) July - 2022 
```{r}
july_2022 <- final_inyection[45,]

july_2022 <- july_2022 %>% 
  mutate(day=1, hour=0) #create the variable day

july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 31), ] #multiplies each row 30 times
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 24), ] #For each day, add 24 hours
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2022 <- july_2022 %>% mutate(elec_inyected =  ener_iny/(31-12))

july_2022 <- july_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change  the electricity inyected from KWh to MWh
```

46) August - 2022 
```{r}
aug_2022 <- final_inyection[46,]

aug_2022 <- aug_2022 %>% mutate(day=1, hour=0) #create the variable day
aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 31), ] #multiplies each row 30 times
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 24), ] #For each day, add 24 hours
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2022 <- aug_2022 %>% mutate(elec_inyected = ener_iny/(31-14))

aug_2022 <- aug_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2022 <- rbind(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
rm(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
```

## Append
Append them and save it

```{r}
final_elec_inyected <- rbind(elec_inyection_2018, elec_inyection_2019, elec_inyection_2020, elec_inyection_2021, elec_inyection_2022)

save(final_elec_inyected, file= 
       paste0(dir$data,"Gurobi/final_elec_inyected_normal.RData"))
```


#Third analysis:

This is to do the graph of microgeneration production 

Use the injection data of electricity into the grid:
1) transform the data from monthly to hourly, and assume the inyected data is uniformy distributed from 8 am to 5 pm
Keep the first row: add it more days and hours

#2018#
1) First row is November - 2018 
```{r}
nov_2018 <- final_inyection[1,]

nov_2018 <- nov_2018 %>% mutate(day=1, hour=0) #create the variable day
nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 30), ] #multiplies each row 30 times
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 24), ] #For each day, add 24 hours
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

#If, the energy inyected is positive, then between 18 pm until 7 am is equal zero, and between 8 am to 17 pm is the electricity inyected/300. 
#Why 23. The first 23, is to find the electricity inyected by day (eliminating those days which the thermal is equal zero)
nov_2018 <- nov_2018 %>% mutate(elec_inyected =  ener_iny/30)

nov_2018 <- nov_2018 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

2) December - 2018
```{r}
dec_2018 <- final_inyection[2,]

dec_2018 <- dec_2018 %>% mutate(day=1, hour=0) #create the variable day
dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 31), ] #multiplies each row 30 times
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 24), ] #For each day, add 24 hours
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2018 <- dec_2018 %>% mutate(elec_inyected =  ener_iny/(31))

dec_2018 <- dec_2018 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


```{r}
elec_inyection_2018 <- rbind(nov_2018, dec_2018)
rm(nov_2018, dec_2018)
```



#2019#
3) January - 2019
```{r}
jan_2019 <- final_inyection[3,]

jan_2019 <- jan_2019 %>% mutate(day=1, hour=0) #create the variable day
jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 31), ] #multiplies each row 30 times
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 24), ] #For each day, add 24 hours
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2019 <- jan_2019 %>% mutate(elec_inyected = ener_iny/(31))

jan_2019 <- jan_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

4) February - 2019
```{r}
feb_2019 <- final_inyection[4,]

feb_2019 <- feb_2019 %>% mutate(day=1, hour=0) #create the variable day
feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 28), ] #multiplies each row 30 times
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 24), ] #For each day, add 24 hours
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2019 <- feb_2019 %>% mutate(elec_inyected =  ener_iny/(28))

feb_2019 <- feb_2019 %>% mutate(elec_inyected= elec_inyected/1000) # change from the electricity inyected from KWh to MWh
```

5) March - 2019
```{r}
mar_2019 <- final_inyection[5,]

mar_2019 <- mar_2019 %>% mutate(day=1, hour=0) #create the variable day
mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 31), ] #multiplies each row 30 times
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 24), ] #For each day, add 24 hours
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2019 <- mar_2019 %>% mutate(elec_inyected = ener_iny/(31))

mar_2019 <- mar_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


6) April - 2019 
```{r}
apr_2019 <- final_inyection[6,]

apr_2019 <- apr_2019 %>% mutate(day=1, hour=0) #create the variable day
apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 30), ] #multiplies each row 30 times
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 24), ] #For each day, add 24 hours
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2019 <- apr_2019 %>% mutate(elec_inyected = ener_iny/(30))

apr_2019 <- apr_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

7) May - 2019
```{r}
may_2019 <- final_inyection[7,]

may_2019 <- may_2019 %>% mutate(day=1, hour=0) #create the variable day
may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 31), ] #multiplies each row 30 times
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 24), ] #For each day, add 24 hours
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2019 <- may_2019 %>% mutate(elec_inyected =  ener_iny/(31))

may_2019 <- may_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

8) June - 2019 
```{r}
june_2019 <- final_inyection[8,]

june_2019 <- june_2019 %>% mutate(day=1, hour=0) #create the variable day
june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 30), ] #multiplies each row 30 times
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 24), ] #For each day, add 24 hours
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2019 <- june_2019 %>% mutate(elec_inyected = ener_iny/(30))

june_2019 <- june_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

9) July - 2019
```{r}
july_2019 <- final_inyection[9,]

july_2019 <- july_2019 %>% mutate(day=1, hour=0) #create the variable day
july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 31), ] #multiplies each row 30 times
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 24), ] #For each day, add 24 hours
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2019 <- july_2019 %>% mutate(elec_inyected =  ener_iny/(31))

july_2019 <- july_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

10) August - 2019 
```{r}
aug_2019 <- final_inyection[10,]

aug_2019 <- aug_2019 %>% mutate(day=1, hour=0) #create the variable day
aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 31), ] #multiplies each row 30 times
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 24), ] #For each day, add 24 hours
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2019 <- aug_2019 %>% mutate(elec_inyected = ener_iny/(31))

aug_2019 <- aug_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

11) September - 2019 
```{r}
sep_2019 <- final_inyection[11,]

sep_2019 <- sep_2019 %>% mutate(day=1, hour=0) #create the variable day
sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 30), ] #multiplies each row 30 times
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 24), ] #For each day, add 24 hours
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2019 <- sep_2019 %>% mutate(elec_inyected =  ener_iny/(30))

sep_2019 <- sep_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

12) October - 2019 
```{r}
oct_2019 <- final_inyection[12,]

oct_2019 <- oct_2019 %>% mutate(day=1, hour=0) #create the variable day
oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 31), ] #multiplies each row 30 times
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% 
  mutate(day=1:31) # add days from 1 to 30

oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 24), ] #For each day, add 24 hours
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2019 <- oct_2019 %>% mutate(elec_inyected = ener_iny/(31))

oct_2019 <- oct_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

13) November - 2019 
```{r}
nov_2019 <- final_inyection[13,]

nov_2019 <- nov_2019 %>% mutate(day=1, hour=0) #create the variable day
nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 30), ] #multiplies each row 30 times
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 24), ] #For each day, add 24 hours
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2019 <- nov_2019 %>% mutate(elec_inyected =  ener_iny/(30))

nov_2019 <- nov_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

14) December - 2019 
```{r}
dec_2019 <- final_inyection[14,]

dec_2019 <- dec_2019 %>% mutate(day=1, hour=0) #create the variable day
dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 31), ] #multiplies each row 30 times
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 24), ] #For each day, add 24 hours
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2019 <- dec_2019 %>% mutate(elec_inyected = ener_iny/(31))

dec_2019 <- dec_2019 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


```{r}
elec_inyection_2019 <- rbind(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
rm(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
```

#2020#
15) January - 2020 
```{r}
jan_2020 <- final_inyection[15,]

jan_2020 <- jan_2020 %>% mutate(day=1, hour=0) #create the variable day
jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 31), ] #multiplies each row 30 times
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 24), ] #For each day, add 24 hours
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2020 <- jan_2020 %>% mutate(elec_inyected =  ener_iny/(31))

jan_2020 <- jan_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

16) February - 2020
```{r}
feb_2020 <- final_inyection[16,]

feb_2020 <- feb_2020 %>% mutate(day=1, hour=0) #create the variable day
feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 29), ] #multiplies each row 30 times
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(day=1:29) # add days from 1 to 30

feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 24), ] #For each day, add 24 hours
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2020 <- feb_2020 %>% mutate(elec_inyected = ener_iny/(29))

feb_2020 <- feb_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

17) March - 2020 
```{r}
mar_2020 <- final_inyection[17,]

mar_2020 <- mar_2020 %>% mutate(day=1, hour=0) #create the variable day
mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 31), ] #multiplies each row 30 times
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 24), ] #For each day, add 24 hours
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2020 <- mar_2020 %>% mutate(elec_inyected = ener_iny/(31))

mar_2020 <- mar_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

18) April 2020 
```{r}
apr_2020 <- final_inyection[18,]

apr_2020 <- apr_2020 %>% mutate(day=1, hour=0) #create the variable day
apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 30), ] #multiplies each row 30 times
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 24), ] #For each day, add 24 hours
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2020 <- apr_2020 %>% mutate(elec_inyected = ener_iny/(30))

apr_2020 <- apr_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

19) May - 2020 
```{r}
may_2020 <- final_inyection[19,]

may_2020 <- may_2020 %>% mutate(day=1, hour=0) #create the variable day
may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 31), ] #multiplies each row 30 times
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 24), ] #For each day, add 24 hours
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2020 <- may_2020 %>% mutate(elec_inyected = ener_iny/(31))

may_2020 <- may_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

20) June 2020 
```{r}
june_2020 <- final_inyection[20,]

june_2020 <- june_2020 %>% mutate(day=1, hour=0) #create the variable day
june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 30), ] #multiplies each row 30 times
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 24), ] #For each day, add 24 hours
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2020 <- june_2020 %>% mutate(elec_inyected = ener_iny/(30))

june_2020 <- june_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```


21) July - 2020 
```{r}
july_2020 <- final_inyection[21,]

july_2020 <- july_2020 %>% mutate(day=1, hour=0) #create the variable day
july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 31), ] #multiplies each row 30 times
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 24), ] #For each day, add 24 hours
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2020 <- july_2020 %>% mutate(elec_inyected = ener_iny/(31))

july_2020 <- july_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

22) August - 2020 
```{r}
aug_2020 <- final_inyection[22,]

aug_2020 <- aug_2020 %>% mutate(day=1, hour=0) #create the variable day
aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 31), ] #multiplies each row 30 times
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 24), ] #For each day, add 24 hours
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2020 <- aug_2020 %>% mutate(elec_inyected = ener_iny/(31))

aug_2020 <- aug_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

23) September 2020 
```{r}
sep_2020 <- final_inyection[23,]

sep_2020 <- sep_2020 %>% mutate(day=1, hour=0) #create the variable day
sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 30), ] #multiplies each row 30 times
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 24), ] #For each day, add 24 hours
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2020 <- sep_2020 %>% mutate(elec_inyected =  ener_iny/(30))

sep_2020 <- sep_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

24) October - 2020 
```{r}
oct_2020 <- final_inyection[24,]

oct_2020 <- oct_2020 %>% mutate(day=1, hour=0) #create the variable day
oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 31), ] #multiplies each row 30 times
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 24), ] #For each day, add 24 hours
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2020 <- oct_2020 %>% mutate(elec_inyected = ener_iny/(31))

oct_2020 <- oct_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

25) November 2020 
```{r}
nov_2020 <- final_inyection[25,]

nov_2020 <- nov_2020 %>% mutate(day=1, hour=0) #create the variable day
nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 30), ] #multiplies each row 30 times
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 24), ] #For each day, add 24 hours
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2020 <- nov_2020 %>% mutate(elec_inyected =  ener_iny/(30))

nov_2020 <- nov_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

26) December - 2020 
```{r}
dec_2020 <- final_inyection[26,]

dec_2020 <- dec_2020 %>% mutate(day=1, hour=0) #create the variable day
dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 31), ] #multiplies each row 30 times
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 24), ] #For each day, add 24 hours
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2020 <- dec_2020 %>% mutate(elec_inyected = ener_iny/(31))

dec_2020 <- dec_2020 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2020 <- rbind(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
rm(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
```

#2021#
27) January - 2021 
```{r}
jan_2021 <- final_inyection[27,]

jan_2021 <- jan_2021 %>% mutate(day=1, hour=0) #create the variable day
jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 31), ] #multiplies each row 30 times
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 24), ] #For each day, add 24 hours
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2021 <- jan_2021 %>% mutate(elec_inyected =  ener_iny/(31))

jan_2021 <- jan_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

28) February - 2021
```{r}
feb_2021 <- final_inyection[28,]

feb_2021 <- feb_2021 %>% mutate(day=1, hour=0) #create the variable day
feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 28), ] #multiplies each row 30 times
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 24), ] #For each day, add 24 hours
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2021 <- feb_2021 %>% mutate(elec_inyected =  ener_iny/(28))

feb_2021 <- feb_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

29) March - 2021 
```{r}
mar_2021 <- final_inyection[29,]

mar_2021 <- mar_2021 %>% mutate(day=1, hour=0) #create the variable day
mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 31), ] #multiplies each row 30 times
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 24), ] #For each day, add 24 hours
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2021 <- mar_2021 %>% mutate(elec_inyected =  ener_iny/31)

mar_2021 <- mar_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

30) April 2021 
```{r}
apr_2021 <- final_inyection[30,]

apr_2021 <- apr_2021 %>% mutate(day=1, hour=0) #create the variable day
apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 30), ] #multiplies each row 30 times
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 24), ] #For each day, add 24 hours
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2021 <- apr_2021 %>% mutate(elec_inyected =  ener_iny/(30))

apr_2021 <- apr_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

31) May - 2021 
```{r}
may_2021 <- final_inyection[31,]

may_2021 <- may_2021 %>% mutate(day=1, hour=0) #create the variable day
may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 31), ] #multiplies each row 30 times
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 24), ] #For each day, add 24 hours
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2021 <- may_2021 %>% mutate(elec_inyected =  ener_iny/(31))

may_2021 <- may_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

32) June 2021 
```{r}
june_2021 <- final_inyection[32,]

june_2021 <- june_2021 %>% mutate(day=1, hour=0) #create the variable day
june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 30), ] #multiplies each row 30 times
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 24), ] #For each day, add 24 hours
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2021 <- june_2021 %>% mutate(elec_inyected =  ener_iny/(30))

june_2021 <- june_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```


33) July - 2021 
```{r}
july_2021 <- final_inyection[33,]

july_2021 <- july_2021 %>% mutate(day=1, hour=0) #create the variable day
july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 31), ] #multiplies each row 30 times
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 24), ] #For each day, add 24 hours
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2021 <- july_2021 %>% mutate(elec_inyected =  ener_iny/(31))

july_2021 <- july_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```

34) August - 2021 
```{r}
aug_2021 <- final_inyection[34,]

aug_2021 <- aug_2021 %>% mutate(day=1, hour=0) #create the variable day
aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 31), ] #multiplies each row 30 times
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 24), ] #For each day, add 24 hours
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2021 <- aug_2021 %>% mutate(elec_inyected = ener_iny/31)

aug_2021 <- aug_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

35) September 2021 
```{r}
sep_2021 <- final_inyection[35,]

sep_2021 <- sep_2021 %>% mutate(day=1, hour=0) #create the variable day
sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 30), ] #multiplies each row 30 times
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 24), ] #For each day, add 24 hours
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2021 <- sep_2021 %>% mutate(elec_inyected =  ener_iny/30)

sep_2021 <- sep_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

36) October - 2021 
```{r}
oct_2021 <- final_inyection[36,]

oct_2021 <- oct_2021 %>% mutate(day=1, hour=0) #create the variable day
oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 31), ] #multiplies each row 30 times
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 24), ] #For each day, add 24 hours
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2021 <- oct_2021 %>% mutate(elec_inyected =  ener_iny/31)

oct_2021 <- oct_2021 %>% mutate(elec_inyected= elec_inyected/1000) # changefrom the electricity inyected from KWh to MWh
```

37) November 2021 
```{r}
nov_2021 <- final_inyection[37,]

nov_2021 <- nov_2021 %>% mutate(day=1, hour=0) #create the variable day
nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 30), ] #multiplies each row 30 times
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 24), ] #For each day, add 24 hours
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2021 <- nov_2021 %>% mutate(elec_inyected =  ener_iny/30)

nov_2021 <- nov_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

38) December - 2021 
```{r}
dec_2021 <- final_inyection[38,]

dec_2021 <- dec_2021 %>% mutate(day=1, hour=0) #create the variable day
dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 31), ] #multiplies each row 30 times
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 24), ] #For each day, add 24 hours
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2021 <- dec_2021 %>% mutate(elec_inyected =  ener_iny/31)

dec_2021 <- dec_2021 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2021 <- rbind(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
rm(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
```

#2022#
39) January - 2022
```{r}
jan_2022 <- final_inyection[39,]

jan_2022 <- jan_2022 %>% mutate(day=1, hour=0) #create the variable day
jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 31), ] #multiplies each row 30 times
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 24), ] #For each day, add 24 hours
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2022 <- jan_2022 %>% mutate(elec_inyected = ener_iny/31)

jan_2022 <- jan_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

40) February - 2022
```{r}
feb_2022 <- final_inyection[40,]

feb_2022 <- feb_2022 %>% mutate(day=1, hour=0) #create the variable day
feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 28), ] #multiplies each row 30 times
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 24), ] #For each day, add 24 hours
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2022 <- feb_2022 %>% mutate(elec_inyected =  ener_iny/28)

feb_2022 <- feb_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

41) March - 2022
```{r}
mar_2022 <- final_inyection[41,]

mar_2022 <- mar_2022 %>% mutate(day=1, hour=0) #create the variable day
mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 31), ] #multiplies each row 30 times
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 24), ] #For each day, add 24 hours
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2022 <- mar_2022 %>% mutate(elec_inyected =  ener_iny/(31))

mar_2022 <- mar_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

42) April 2022 
```{r}
apr_2022 <- final_inyection[42,]

apr_2022 <- apr_2022 %>% mutate(day=1, hour=0) #create the variable day
apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 30), ] #multiplies each row 30 times
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 24), ] #For each day, add 24 hours
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2022 <- apr_2022 %>% mutate(elec_inyected =  ener_iny/(30))

apr_2022 <- apr_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

43) May - 2022 
```{r}
may_2022 <- final_inyection[43,]

may_2022 <- may_2022 %>% mutate(day=1, hour=0) #create the variable day
may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 31), ] #multiplies each row 30 times
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 24), ] #For each day, add 24 hours
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2022 <- may_2022 %>% mutate(elec_inyected =  ener_iny/(31))

may_2022 <- may_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

44) June 2022 
```{r}
june_2022 <- final_inyection[44,]

june_2022 <- june_2022 %>% mutate(day=1, hour=0) #create the variable day
june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 30), ] #multiplies each row 30 times
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 24), ] #For each day, add 24 hours
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2022 <- june_2022 %>% mutate(elec_inyected =  ener_iny/(30))

june_2022 <- june_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change the electricity inyected from KWh to MWh
```


45) July - 2022 
```{r}
july_2022 <- final_inyection[45,]

july_2022 <- july_2022 %>% mutate(day=1, hour=0) #create the variable day
july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 31), ] #multiplies each row 30 times
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 24), ] #For each day, add 24 hours
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2022 <- july_2022 %>% mutate(elec_inyected =  ener_iny/(31))

july_2022 <- july_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change  the electricity inyected from KWh to MWh
```

46) August - 2022 
```{r}
aug_2022 <- final_inyection[46,]

aug_2022 <- aug_2022 %>% mutate(day=1, hour=0) #create the variable day
aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 31), ] #multiplies each row 30 times
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 24), ] #For each day, add 24 hours
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2022 <- aug_2022 %>% mutate(elec_inyected = ener_iny/(31))

aug_2022 <- aug_2022 %>% mutate(elec_inyected= elec_inyected/1000) #change from the electricity inyected from KWh to MWh
```

```{r}
elec_inyection_2022 <- rbind(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
rm(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
```

append them and save it
```{r}
final_elec_inyected <- rbind(elec_inyection_2018, elec_inyection_2019, elec_inyection_2020, elec_inyection_2021, elec_inyection_2022)

save(final_elec_inyected, file= "C:/Users/natal/OneDrive/Documents/Net_metering_UY/Gurobi/final_elec_inyected_graph.RData")
```
