---
title:   "Microgenerators: Descriptive Statistics"
authors: "Natalia D'Agosti & Facundo Danza" 
---


# Load the packages

First, we load the necessary pacakges:
```{r}
rm(list=ls())
gc()
```

Second, we load the packages
```{r}
# install.packages("pacman")
pacman::p_load(tidyverse, readxl, lubridate, margins,
               sandwich, arm, fixest, gapminder, 
               #sunab, 
               car, fplot, did)
```

Third, we set the plotting theme:
```{r}
theme_set(theme_bw())
```

Then, we load the directories:
```{r}
dir        <- list()
dir$root   <- dirname(getwd())
dir$data   <- paste0(dirname(getwd()), "/data/")
dir$fig    <- paste0(dirname(getwd()), "/figures/")
dir$tab    <- paste0(dirname(getwd()), "/tables/")
```


# Clean the databases

Upload the data
```{r}
MG_data <- 
  read_excel(paste0(dir$data,"data/Documento 3.xlsx"))
```

```{r}
names(MG_data) <- 
  c("ID", 
    "capacity_w", 
    "state", 
    "tariff", 
    "installation_date", 
    "type", 
    "capacity_hired", 
    paste0("kwh_month_minus", 1:12))
```

## Count the number of solar panels
```{r}
MG_data = 
  MG_data %>% 
  mutate(inst_date = as.Date(installation_date))

MG_data$inst_month_yr <- format(
  as.Date(MG_data$inst_date), "%Y-%m")
```

In our paper, we keep data until 2022; we thus exclude the rest of the sample:
```{r}
# we want to study capacity for the years in which we have better data
MG_data = 
  MG_data %>% 
  mutate(year = 
           year(installation_date), 
         month = 
           month(installation_date))

MG_data = 
  MG_data
```


```{r}
x_label = "2010-01"

for (i in seq(2012,2024,2)) {
  x_label = c(x_label, paste0(i,"-01"))
}

plot_new_micro2 <- MG_data %>%
  filter(type == "NEGOCIO") %>%
  group_by(inst_month_yr) %>% 
  summarise(sum_n = n()) %>%
  ggplot(aes(x=inst_month_yr, y=sum_n, 
             color="New Solar"), size=2) +
  geom_point(size=2, color="darkgray") + 
  theme(text = element_text(size = 15)) + 
  labs(y = "Solar Panel Installations" ,x = "Date") + 
  scale_x_discrete(breaks = x_label) +
  theme(legend.key.size = unit(1, 'cm'))

plot_new_micro2
```

```{r}
ggsave(paste0(dir$fig,"plot_new_micro3.png"), 
              width = 7, height = 4.5)
```

## Evolution of capacity

```{r}
x_label = "2010-01"

for (i in seq(2012,2024,2)) {
  x_label = c(x_label, paste0(i,"-01"))
}

plot_new_micro2 <- MG_data %>%
  filter(type == "NEGOCIO") %>%
  group_by(inst_month_yr) %>% 
  summarise(avg_capacity = 
              mean(capacity_hired, na.rm = T)) %>%
  ggplot(aes(x=inst_month_yr, 
             y=avg_capacity), size=2) +
  geom_point(size=2, 
           color="darkgray") +
  theme(text = element_text(size = 15)) + 
  labs(y = "Solar Panel Capacity (kW)",
       x = "Date") + 
  scale_x_discrete(breaks = x_label) +
  theme(legend.key.size = unit(1, 'cm'))

plot_new_micro2
```

```{r}
ggsave(paste0(dir$fig,"plot_micro_capacity.png"), 
              width = 7, height = 4.5)
```

### Regression analysis

```{r}
reg_capacity <- feols(
  I(capacity_hired) ~ I(year-2011),
  cluster = "year",
  data = MG_data %>%
    filter(type == "NEGOCIO" & 
             !is.na(year))
)

etable(reg_capacity)
```


## Tariff of each business
```{r}
MG_data_firms = 
  MG_data %>% 
  filter(type == "NEGOCIO") %>%
  arrange(installation_date)
```

Percentage of each tariff:
```{r}
all_tariffs = 
  unique(MG_data_firms$tariff)
```

```{r}
MG_data_firms_clean = 
  MG_data_firms %>% 
  filter(installation_date <+ as.Date("10-01-2022"))
```

```{r}
for (t in all_tariffs) {
  print(paste0("Percentage of ", t, " tariff is ",
        MG_data_firms %>%
          summarise(percentage = mean(tariff == t)))[[1]])

}
```

## Firm type

```{r}
firm_type = 
  read_excel(paste0(dir$data, "constructed_data/firm_names_manual.xls"))
```

```{r}
all_types = 
  unique(firm_type$Type)
```

```{r}
for (t in all_types) {
  print(paste0("Percentage of ", t, " is ",
        firm_type %>%
          summarise(percentage = mean(Type == t, na.rm = T)))[[1]])

}
```

```{r}
firm_type %>%
  filter(Type == "Commercial") %>%
  summarise(percentage = mean(SA, na.rm = T))
```

```{r}
table(firm_type$Industry)/sum(!is.na(firm_type$Industry))
```



