Arrange the Co2 data to use it in the Gurobi optimization problem.

The data of Co2 is at monthly level. Thus, transform/distribute it to hourly level. 
And then find the emission factor by MW 1) constant 2)different given the amount of thermal produced


```{r}
rm(list=ls())
library(dplyr)
library(readxl)
```


```{r}
load("C:/Users/natal/OneDrive - University of Edinburgh/Net_metering_UY/Final_project/Gurobi/final_co2.RData")
```

Eliminate the variables that I dont need:
```{r}
co2 <- final_co2 %>% dplyr::select(c("year", "month", "day", "prod", "prod_gas", "own_consum", "gasoil_consum", "gas_consum", "gas_spe_consum", "gas_spe_consum_2", "fueloil_consum", "fuelmot_consum", "fuel_oil", "fueloil_tj", "gasoil_tj", "fueloil_co2", "gasoil_co2", "ng_co2", "total_co2", "desc_co2"))
```

Filter the year 2018, 2019, 2020, 2021, and 2022
```{r}
co2 <- co2 %>% filter(year>2017) %>% dplyr::distinct()
#check <- final_co2 %>% dplyr::select(c("year", "month", "day", "prod", "prod_gas", "own_consum", "gasoil_consum", "gas_consum", "gas_spe_consum", "gas_spe_consum_2", "fueloil_consum", "fuelmot_consum", "fuel_oil", "fueloil_tj", "gasoil_tj", "fueloil_co2", "gasoil_co2", "ng_co2", "total_co2", "desc_co2")) %>% filter(year>2017)
```

#2018#
1) First row is November - 2018 
```{r}
nov_2018 <- co2[3,]

nov_2018 <- nov_2018 %>% mutate(day=1, hour=0) #create the variable day
nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 30), ] #multiplies each row 30 times
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2018 <- nov_2018[rep(seq_len(nrow(nov_2018)), each = 24), ] #For each day, add 24 hours
nov_2018 <- nov_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2018 <- nov_2018 %>% mutate(day_co2=(desc_co2/(30-7))) #Why 30 -7: because there are 7 days there is no thermal production
```

2) December - 2018
```{r}
dec_2018 <- co2[4,]

dec_2018 <- dec_2018 %>% mutate(day=1, hour=0) #create the variable day
dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 31), ] #multiplies each row 30 times
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2018 <- dec_2018[rep(seq_len(nrow(dec_2018)), each = 24), ] #For each day, add 24 hours
dec_2018 <- dec_2018 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2018 <- dec_2018 %>% mutate(day_co2=(desc_co2/(31-5))) #Why 31-5: because there are 5 days there is no thermal production
```


```{r}
co2_2018 <- rbind(nov_2018, dec_2018)
rm(nov_2018, dec_2018)
```



#2019#
3) January - 2019
```{r}
jan_2019 <- co2[13,]

jan_2019 <- jan_2019 %>% mutate(day=1, hour=0) #create the variable day
jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 31), ] #multiplies each row 30 times
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2019 <- jan_2019[rep(seq_len(nrow(jan_2019)), each = 24), ] #For each day, add 24 hours
jan_2019 <- jan_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2019 <- jan_2019 %>% mutate(day_co2=(desc_co2/(31-2)))
```

4) February - 2019
```{r}
feb_2019 <- co2[17,]

feb_2019 <- feb_2019 %>% mutate(day=1, hour=0) #create the variable day
feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 28), ] #multiplies each row 30 times
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2019 <- feb_2019[rep(seq_len(nrow(feb_2019)), each = 24), ] #For each day, add 24 hours
feb_2019 <- feb_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2019 <- feb_2019 %>% mutate(day_co2=(desc_co2/(28-2)))
```

5) March - 2019
```{r}
mar_2019 <- co2[18,]

mar_2019 <- mar_2019 %>% mutate(day=1, hour=0) #create the variable day
mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 31), ] #multiplies each row 30 times
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2019 <- mar_2019[rep(seq_len(nrow(mar_2019)), each = 24), ] #For each day, add 24 hours
mar_2019 <- mar_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2019 <- mar_2019 %>% mutate(day_co2=(desc_co2/(31-10)))
```

6) April - 2019 
```{r}
apr_2019 <- co2[19,]

apr_2019 <- apr_2019 %>% mutate(day=1, hour=0) #create the variable day
apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 30), ] #multiplies each row 30 times
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2019 <- apr_2019[rep(seq_len(nrow(apr_2019)), each = 24), ] #For each day, add 24 hours
apr_2019 <- apr_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2019 <- apr_2019 %>% mutate(day_co2=(desc_co2/(30-20)))
```

7) May - 2019
```{r}
may_2019 <- co2[20,]

may_2019 <- may_2019 %>% mutate(day=1, hour=0) #create the variable day
may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 31), ] #multiplies each row 30 times
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2019 <- may_2019[rep(seq_len(nrow(may_2019)), each = 24), ] #For each day, add 24 hours
may_2019 <- may_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2019 <- may_2019 %>% mutate(day_co2=(desc_co2/(31-19)))
```

8) June - 2019 
```{r}
june_2019 <- co2[21,]

june_2019 <- june_2019 %>% mutate(day=1, hour=0) #create the variable day
june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 30), ] #multiplies each row 30 times
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2019 <- june_2019[rep(seq_len(nrow(june_2019)), each = 24), ] #For each day, add 24 hours
june_2019 <- june_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2019 <- june_2019 %>% mutate(day_co2=(desc_co2/(30-18)))
```

9) July - 2019
```{r}
july_2019 <- co2[22,]

july_2019 <- july_2019 %>% mutate(day=1, hour=0) #create the variable day
july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 31), ] #multiplies each row 30 times
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2019 <- july_2019[rep(seq_len(nrow(july_2019)), each = 24), ] #For each day, add 24 hours
july_2019 <- july_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2019 <- july_2019 %>% mutate(day_co2=(desc_co2/(31-15)))
```

10) August - 2019 
```{r}
aug_2019 <- co2[23,]

aug_2019 <- aug_2019 %>% mutate(day=1, hour=0) #create the variable day
aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 31), ] #multiplies each row 30 times
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2019 <- aug_2019[rep(seq_len(nrow(aug_2019)), each = 24), ] #For each day, add 24 hours
aug_2019 <- aug_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2019 <- aug_2019 %>% mutate(day_co2=(desc_co2/(31-12)))
```

11) September - 2019 
```{r}
sep_2019 <- co2[24,]

sep_2019 <- sep_2019 %>% mutate(day=1, hour=0) #create the variable day
sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 30), ] #multiplies each row 30 times
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2019 <- sep_2019[rep(seq_len(nrow(sep_2019)), each = 24), ] #For each day, add 24 hours
sep_2019 <- sep_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2019 <- sep_2019 %>% mutate(day_co2=(desc_co2/(30-7)))
```

12) October - 2019 
```{r}
oct_2019 <- co2[14,]

oct_2019 <- oct_2019 %>% mutate(day=1, hour=0) #create the variable day
oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 31), ] #multiplies each row 30 times
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2019 <- oct_2019[rep(seq_len(nrow(oct_2019)), each = 24), ] #For each day, add 24 hours
oct_2019 <- oct_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2019 <- oct_2019 %>% mutate(day_co2=(desc_co2/(31-12)))
```

13) November - 2019 
```{r}
nov_2019 <- co2[15,]

nov_2019 <- nov_2019 %>% mutate(day=1, hour=0) #create the variable day
nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 30), ] #multiplies each row 30 times
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2019 <- nov_2019[rep(seq_len(nrow(nov_2019)), each = 24), ] #For each day, add 24 hours
nov_2019 <- nov_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2019 <- nov_2019 %>% mutate(day_co2=(desc_co2/(30-20)))
```

14) December - 2019 
```{r}
dec_2019 <- co2[16,]

dec_2019 <- dec_2019 %>% mutate(day=1, hour=0) #create the variable day
dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 31), ] #multiplies each row 30 times
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2019 <- dec_2019[rep(seq_len(nrow(dec_2019)), each = 24), ] #For each day, add 24 hours
dec_2019 <- dec_2019 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2019 <- dec_2019 %>% mutate(day_co2=(desc_co2/(31-21)))
```


```{r}
co2_2019 <- rbind(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
rm(jan_2019, feb_2019, mar_2019, apr_2019, may_2019, june_2019, july_2019, aug_2019, sep_2019, oct_2019, nov_2019, dec_2019)
```

#2020#
15) January - 2020 
```{r}
jan_2020 <- co2[25,]

jan_2020 <- jan_2020 %>% mutate(day=1, hour=0) #create the variable day
jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 31), ] #multiplies each row 30 times
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2020 <- jan_2020[rep(seq_len(nrow(jan_2020)), each = 24), ] #For each day, add 24 hours
jan_2020 <- jan_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2020 <- jan_2020 %>% mutate(day_co2=(desc_co2/(31-15)))
```

16) February - 2020
```{r}
feb_2020 <- co2[29,]

feb_2020 <- feb_2020 %>% mutate(day=1, hour=0) #create the variable day
feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 29), ] #multiplies each row 30 times
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(day=1:29) # add days from 1 to 30

feb_2020 <- feb_2020[rep(seq_len(nrow(feb_2020)), each = 24), ] #For each day, add 24 hours
feb_2020 <- feb_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2020 <- feb_2020 %>% mutate(day_co2=(desc_co2/(29-9)))
```

17) March - 2020 
```{r}
mar_2020 <- co2[30,]

mar_2020 <- mar_2020 %>% mutate(day=1, hour=0) #create the variable day
mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 31), ] #multiplies each row 30 times
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2020 <- mar_2020[rep(seq_len(nrow(mar_2020)), each = 24), ] #For each day, add 24 hours
mar_2020 <- mar_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2020 <- mar_2020 %>% mutate(day_co2=(desc_co2/(31-9)))
```

18) April 2020 
```{r}
apr_2020 <- co2[31,]

apr_2020 <- apr_2020 %>% mutate(day=1, hour=0) #create the variable day
apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 30), ] #multiplies each row 30 times
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2020 <- apr_2020[rep(seq_len(nrow(apr_2020)), each = 24), ] #For each day, add 24 hours
apr_2020 <- apr_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2020 <- apr_2020 %>% mutate(day_co2=(desc_co2/(30-23)))
```

19) May - 2020 
```{r}
may_2020 <- co2[32,]

may_2020 <- may_2020 %>% mutate(day=1, hour=0) #create the variable day
may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 31), ] #multiplies each row 30 times
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2020 <- may_2020[rep(seq_len(nrow(may_2020)), each = 24), ] #For each day, add 24 hours
may_2020 <- may_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2020 <- may_2020 %>% mutate(day_co2=(desc_co2/(31-25)))
```

20) June 2020 
```{r}
june_2020 <- co2[33,]

june_2020 <- june_2020 %>% mutate(day=1, hour=0) #create the variable day
june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 30), ] #multiplies each row 30 times
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2020 <- june_2020[rep(seq_len(nrow(june_2020)), each = 24), ] #For each day, add 24 hours
june_2020 <- june_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2020 <- june_2020 %>% mutate(day_co2=(desc_co2/(30-17)))
```


21) July - 2020 
```{r}
july_2020 <- co2[34,]

july_2020 <- july_2020 %>% mutate(day=1, hour=0) #create the variable day
july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 31), ] #multiplies each row 30 times
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2020 <- july_2020[rep(seq_len(nrow(july_2020)), each = 24), ] #For each day, add 24 hours
july_2020 <- july_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2020 <- july_2020 %>% mutate(day_co2=(desc_co2/(31-14)))
```

22) August - 2020 
```{r}
aug_2020 <- co2[35,]

aug_2020 <- aug_2020 %>% mutate(day=1, hour=0) #create the variable day
aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 31), ] #multiplies each row 30 times
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2020 <- aug_2020[rep(seq_len(nrow(aug_2020)), each = 24), ] #For each day, add 24 hours
aug_2020 <- aug_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2020 <- aug_2020 %>% mutate(day_co2=(desc_co2/(31-21)))
```

23) September 2020 
```{r}
sep_2020 <- co2[36,]

sep_2020 <- sep_2020 %>% mutate(day=1, hour=0) #create the variable day
sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 30), ] #multiplies each row 30 times
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2020 <- sep_2020[rep(seq_len(nrow(sep_2020)), each = 24), ] #For each day, add 24 hours
sep_2020 <- sep_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2020 <- sep_2020 %>% mutate(day_co2=(desc_co2/(30-24)))
```

24) October - 2020 
```{r}
oct_2020 <- co2[26,]

oct_2020 <- oct_2020 %>% mutate(day=1, hour=0) #create the variable day
oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 31), ] #multiplies each row 30 times
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2020 <- oct_2020[rep(seq_len(nrow(oct_2020)), each = 24), ] #For each day, add 24 hours
oct_2020 <- oct_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2020 <- oct_2020 %>% mutate(day_co2=(desc_co2/(31-12)))
```

25) November 2020 
```{r}
nov_2020 <- co2[27,]

nov_2020 <- nov_2020 %>% mutate(day=1, hour=0) #create the variable day
nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 30), ] #multiplies each row 30 times
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2020 <- nov_2020[rep(seq_len(nrow(nov_2020)), each = 24), ] #For each day, add 24 hours
nov_2020 <- nov_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2020 <- nov_2020 %>% mutate(day_co2=(desc_co2/(30-3)))
```

26) December - 2020 
```{r}
dec_2020 <- co2[28,]

dec_2020 <- dec_2020 %>% mutate(day=1, hour=0) #create the variable day
dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 31), ] #multiplies each row 30 times
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2020 <- dec_2020[rep(seq_len(nrow(dec_2020)), each = 24), ] #For each day, add 24 hours
dec_2020 <- dec_2020 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2020 <- dec_2020 %>% mutate(day_co2=(desc_co2/(31-2)))
```

```{r}
co2_2020 <- rbind(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
rm(jan_2020, feb_2020, mar_2020, apr_2020, may_2020, june_2020, july_2020, aug_2020, sep_2020, oct_2020, nov_2020, dec_2020)
```

#2021#
27) January - 2021 
```{r}
jan_2021 <- co2[37,]

jan_2021 <- jan_2021 %>% mutate(day=1, hour=0) #create the variable day
jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 31), ] #multiplies each row 30 times
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2021 <- jan_2021[rep(seq_len(nrow(jan_2021)), each = 24), ] #For each day, add 24 hours
jan_2021 <- jan_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2021 <- jan_2021 %>% mutate(day_co2=(desc_co2/(31-5)))
```

28) February - 2021
```{r}
feb_2021 <- co2[41,]

feb_2021 <- feb_2021 %>% mutate(day=1, hour=0) #create the variable day
feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 28), ] #multiplies each row 30 times
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2021 <- feb_2021[rep(seq_len(nrow(feb_2021)), each = 24), ] #For each day, add 24 hours
feb_2021 <- feb_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2021 <- feb_2021 %>% mutate(day_co2=(desc_co2/(28-9)))
```

29) March - 2021 
```{r}
mar_2021 <- co2[42,]

mar_2021 <- mar_2021 %>% mutate(day=1, hour=0) #create the variable day
mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 31), ] #multiplies each row 30 times
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2021 <- mar_2021[rep(seq_len(nrow(mar_2021)), each = 24), ] #For each day, add 24 hours
mar_2021 <- mar_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2021 <- mar_2021 %>% mutate(day_co2=(desc_co2/31))
```

30) April 2021 
```{r}
apr_2021 <- co2[43,]

apr_2021 <- apr_2021 %>% mutate(day=1, hour=0) #create the variable day
apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 30), ] #multiplies each row 30 times
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2021 <- apr_2021[rep(seq_len(nrow(apr_2021)), each = 24), ] #For each day, add 24 hours
apr_2021 <- apr_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2021 <- apr_2021 %>% mutate(day_co2=(desc_co2/(30-7)))
```

31) May - 2021 
```{r}
may_2021 <- co2[44,]

may_2021 <- may_2021 %>% mutate(day=1, hour=0) #create the variable day
may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 31), ] #multiplies each row 30 times
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2021 <- may_2021[rep(seq_len(nrow(may_2021)), each = 24), ] #For each day, add 24 hours
may_2021 <- may_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2021 <- may_2021 %>% mutate(day_co2=(desc_co2/(31-4)))
```

32) June 2021 
```{r}
june_2021 <- co2[45,]

june_2021 <- june_2021 %>% mutate(day=1, hour=0) #create the variable day
june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 30), ] #multiplies each row 30 times
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2021 <- june_2021[rep(seq_len(nrow(june_2021)), each = 24), ] #For each day, add 24 hours
june_2021 <- june_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2021 <- june_2021 %>% mutate(day_co2=(desc_co2/(30-7)))
```


33) July - 2021 
```{r}
july_2021 <- co2[46,]

july_2021 <- july_2021 %>% mutate(day=1, hour=0) #create the variable day
july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 31), ] #multiplies each row 30 times
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2021 <- july_2021[rep(seq_len(nrow(july_2021)), each = 24), ] #For each day, add 24 hours
july_2021 <- july_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2021 <- july_2021 %>% mutate(day_co2=(desc_co2/(31-7)))
```

34) August - 2021 
```{r}
aug_2021 <- co2[47,]

aug_2021 <- aug_2021 %>% mutate(day=1, hour=0) #create the variable day
aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 31), ] #multiplies each row 30 times
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2021 <- aug_2021[rep(seq_len(nrow(aug_2021)), each = 24), ] #For each day, add 24 hours
aug_2021 <- aug_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2021 <- aug_2021 %>% mutate(day_co2=(desc_co2/31))
```

35) September 2021 
```{r}
sep_2021 <- co2[48,]

sep_2021 <- sep_2021 %>% mutate(day=1, hour=0) #create the variable day
sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 30), ] #multiplies each row 30 times
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

sep_2021 <- sep_2021[rep(seq_len(nrow(sep_2021)), each = 24), ] #For each day, add 24 hours
sep_2021 <- sep_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

sep_2021 <- sep_2021 %>% mutate(day_co2=(desc_co2/30))
```

36) October - 2021 
```{r}
oct_2021 <- co2[38,]

oct_2021 <- oct_2021 %>% mutate(day=1, hour=0) #create the variable day
oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 31), ] #multiplies each row 30 times
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

oct_2021 <- oct_2021[rep(seq_len(nrow(oct_2021)), each = 24), ] #For each day, add 24 hours
oct_2021 <- oct_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

oct_2021 <- oct_2021 %>% mutate(day_co2=(desc_co2/31))
```

37) November 2021 
```{r}
nov_2021 <- co2[39,]

nov_2021 <- nov_2021 %>% mutate(day=1, hour=0) #create the variable day
nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 30), ] #multiplies each row 30 times
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

nov_2021 <- nov_2021[rep(seq_len(nrow(nov_2021)), each = 24), ] #For each day, add 24 hours
nov_2021 <- nov_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

nov_2021 <- nov_2021 %>% mutate(day_co2=(desc_co2/30))
```

38) December - 2021 
```{r}
dec_2021 <- co2[40,]

dec_2021 <- dec_2021 %>% mutate(day=1, hour=0) #create the variable day
dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 31), ] #multiplies each row 30 times
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

dec_2021 <- dec_2021[rep(seq_len(nrow(dec_2021)), each = 24), ] #For each day, add 24 hours
dec_2021 <- dec_2021 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

dec_2021 <- dec_2021 %>% mutate(day_co2=(desc_co2/31))
```

```{r}
co2_2021 <- rbind(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
rm(jan_2021, feb_2021, mar_2021, apr_2021, may_2021, june_2021, july_2021, aug_2021, sep_2021, oct_2021, nov_2021, dec_2021)
```

#2022#
39) January - 2022
```{r}
jan_2022 <- co2[49,]

jan_2022 <- jan_2022 %>% mutate(day=1, hour=0) #create the variable day
jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 31), ] #multiplies each row 30 times
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

jan_2022 <- jan_2022[rep(seq_len(nrow(jan_2022)), each = 24), ] #For each day, add 24 hours
jan_2022 <- jan_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

jan_2022 <- jan_2022 %>% mutate(day_co2=(desc_co2/31))
```

40) February - 2022
```{r}
feb_2022 <- co2[50,]

feb_2022 <- feb_2022 %>% mutate(day=1, hour=0) #create the variable day
feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 28), ] #multiplies each row 30 times
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(day=1:28) # add days from 1 to 30

feb_2022 <- feb_2022[rep(seq_len(nrow(feb_2022)), each = 24), ] #For each day, add 24 hours
feb_2022 <- feb_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

feb_2022 <- feb_2022 %>% mutate(day_co2=(desc_co2/28))
```

41) March - 2022
```{r}
mar_2022 <- co2[51,]

mar_2022 <- mar_2022 %>% mutate(day=1, hour=0) #create the variable day
mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 31), ] #multiplies each row 30 times
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

mar_2022 <- mar_2022[rep(seq_len(nrow(mar_2022)), each = 24), ] #For each day, add 24 hours
mar_2022 <- mar_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

mar_2022 <- mar_2022 %>% mutate(day_co2=(desc_co2/(31-3)))
```

42) April 2022 
```{r}
apr_2022 <- co2[52,]

apr_2022 <- apr_2022 %>% mutate(day=1, hour=0) #create the variable day
apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 30), ] #multiplies each row 30 times
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

apr_2022 <- apr_2022[rep(seq_len(nrow(apr_2022)), each = 24), ] #For each day, add 24 hours
apr_2022 <- apr_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

apr_2022 <- apr_2022 %>% mutate(day_co2=(desc_co2/(30-17)))
```

43) May - 2022 
```{r}
may_2022 <- co2[53,]

may_2022 <- may_2022 %>% mutate(day=1, hour=0) #create the variable day
may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 31), ] #multiplies each row 30 times
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

may_2022 <- may_2022[rep(seq_len(nrow(may_2022)), each = 24), ] #For each day, add 24 hours
may_2022 <- may_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

may_2022 <- may_2022 %>% mutate(day_co2=(desc_co2/(31-11)))
```

44) June 2022 
```{r}
june_2022 <- co2[54,]

june_2022 <- june_2022 %>% mutate(day=1, hour=0) #create the variable day
june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 30), ] #multiplies each row 30 times
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(day=1:30) # add days from 1 to 30

june_2022 <- june_2022[rep(seq_len(nrow(june_2022)), each = 24), ] #For each day, add 24 hours
june_2022 <- june_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

june_2022 <- june_2022 %>% mutate(day_co2=(desc_co2/(30-5)))
```


45) July - 2022 
```{r}
july_2022 <- co2[55,]

july_2022 <- july_2022 %>% mutate(day=1, hour=0) #create the variable day
july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 31), ] #multiplies each row 30 times
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

july_2022 <- july_2022[rep(seq_len(nrow(july_2022)), each = 24), ] #For each day, add 24 hours
july_2022 <- july_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

july_2022 <- july_2022 %>% mutate(day_co2=(desc_co2/(31-12)))
```

46) August - 2022 
```{r}
aug_2022 <- co2[56,]

aug_2022 <- aug_2022 %>% mutate(day=1, hour=0) #create the variable day
aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 31), ] #multiplies each row 30 times
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(day=1:31) # add days from 1 to 30

aug_2022 <- aug_2022[rep(seq_len(nrow(aug_2022)), each = 24), ] #For each day, add 24 hours
aug_2022 <- aug_2022 %>% group_by(year, month, day) %>% mutate(hour=0:23) # to each day, add 0 to 23 hours

aug_2022 <- aug_2022 %>% mutate(day_co2=(desc_co2/(31-14)))
```

```{r}
co2_2022 <- rbind(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
rm(jan_2022, feb_2022, mar_2022, apr_2022, may_2022, june_2022, july_2022, aug_2022)
```

append them and save it
```{r}
final_co2_G <- rbind(co2_2018, co2_2019, co2_2020, co2_2021, co2_2022)

save(final_co2_G, file= "C:/Users/natal/OneDrive - University of Edinburgh/Net_metering_UY/Final_project/Gurobi/final_co2_G.RData")
```


